\cvsection{Academic Projects - B.S.}
    
\cvevent{Heat Transfer Project}{Shiraz University}{Fall 2019}{}
In this project I've numerically analyzed the heat transfer in a duct. \\
\textbf{Advisor: Dr.} Mehdi Bahneshi.\\ 
\vspace{5pt}
\cvevent{Robotics Project}{Shiraz University}{Fall 2020}{}
In this project we designed and simulate a quad-rotor with a capability of transforming to a mobile robot.\\
\textbf{Advisor: Dr.} Hossein Mohammadi\\
\vspace{5pt}

\cvevent{Mechanism design Project}{Shiraz University}{Spring 2021}{}
In this project we asked to design and Simulate a wire-wrapping tool for the usage in the construction industry.\\
\textbf{Advisor: Dr.} Sajjad Taghvaei.\\
\vspace{5pt} 
\cvevent{Introduction to Mechatronics Project}{Shiraz University}{Spring 2021}{}
In this project we made a color-detection sensor.\\
\textbf{Advisor: Prof.} Mohammad Eghtesad\\
\vspace{5pt}
\cvevent{Introduction to Bio-Mechanics}{Shiraz University}{Fall 2021}{}
In this project i've done mechanical design of a hospital bed.\\
\textbf{Advisor: Dr.} Sajjad Taghvaei\\
\vspace{5pt}
\cvevent{Batchlor's Degree Final Project}{Shiraz University}{Fall 2021}{}
\begin{small}
    In this project I've designed an IOT garden. In this project the user can control a garden using a web interface and scheduled for watering. All the programming and PCB design is done by me.\\
\end{small}
\textbf{Supervisor Prof.} Mohammad Eghtesad. \\
\vspace{5pt}
\cvsection{Refrences}
Available on request.
% \begin{itemize}
    % \item \textbf{Mahmood Mazare} \\ Researcher at University of Georgia \\ \email{\href{mailto:mahmood.mazare@gmail.com}{Email}}
    % \item \textbf{Mostafa Taghizadeh Shol} \\ Associate Professor at Shahid Beheshti University \\  \email{\href{mailto:mo_tagizadeh@sbu.ac.ir}{mo\_tagizadeh@sbu.ac.ir}}
    % \item \textbf{Hadi Asharioun} \\ Assistant Professor at Shahid Beheshti University\\ \email{\href{mailto:asharioun@sbu.ac.ir}{asharioun@sbu.ac.ir}}
    % \item \textbf{Sajjad Taghvaei} \\ Associate Professor at Shiraz University \\ \email{\href{mailto:sj.taghvaei@shirazu.ac.ir}{sj.taghvaei@shirazu.ac.ir}}
    % \item \textbf{Mohammadreza Haghjo} \\ Assistant Professor as Shahid Beheshti University \\ \email{\href{mailto:m_haghjoo@sbu.ac.ir}{m\_haghjoo@sbu.ac.ir}}
    
% \end{itemize}
